---
output: github_document
bibliography: ["packages.bib", "PAGES.bib"]
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# PAGES

<!-- badges: start -->
<!-- badges: end -->

The goal of PAGES is to ...

```{r pkgs, echo=FALSE, message=FALSE}
# following code for loading and writing the bibtex references for the used pkgs
pkgs <- c("dplyr", "tidyr", "tibble", "stringr", "readr", "magrittr",
          "ggplot2", "purrr", "devtools", 
          "roxygen2", "knitr", "rmarkdown",
          "marelac", "datasauRus", "thematic")    
# Get the R reference
rref <- citation()
# Create ref key
rref$key <- "rversion"
hadley <- bibentry(
  key = "Wickham2015",
  bibtype = "Book",
  title = "R packages: organize, test, document, and share your code",
  author =  person("Hadley","Wickham"),
  year = "2015",
  publisher = " O'Reilly Media, Inc.",
  url = "https://r-pkgs.org/"
  )
knitr::write_bib(pkgs, "packages.bib", prefix = "")
pkgs <- bibtex::read.bib("packages.bib")
bibtex::write.bib(
  purrr::reduce(list(rref, hadley, pkgs), append), 
  file = "packages.bib"
  )
# copy vignettes
fs::file_copy(
  fs::path("PAGES", ext = "bib"), 
  fs::path("vignettes/PAGES", ext = "bib"), 
  overwrite = TRUE
  )
fs::file_copy(
  fs::path("packages", ext = "bib"), 
  fs::path("vignettes/packages", ext = "bib"), 
  overwrite = TRUE
  )
# copy presentation
fs::file_copy(
  fs::path("PAGES", ext = "bib"), 
  fs::path("inst", "presentation", "PAGES", ext = "bib"), 
  overwrite = TRUE
  )
fs::file_copy(
  fs::path("packages", ext = "bib"), 
  fs::path("inst", "presentation", "packages", ext = "bib"), 
  overwrite = TRUE
  )
```


## Credits

The construction of the R [@rversion] package *point* and associated documentation was aided by the packages; *devtools* [@devtools], *roxygen2* [@roxygen2], *knitr* [@knitr2014 ; @knitr2015], *rmarkdown* [@rmarkdown2018; @rmarkdown2020] and the superb guidance in the book: *R packages: organize, test, document, and share your code*, by @Wickham2015. In addition, this package relies on a set of external packages from the tidyverse universe, including: *dplyr* [@dplyr], *tidyr* [@tidyr], *tibble* [@tibble], *stringr* [@stringr], *readr* [@readr], *magrittr* [@magrittr], *readr* [@readr], and *purrr* [@purrr]. Plots are made with *ggplot2* [@ggplot22016] and *thematic* [@thematic] is used for a consistent design in the presentation.


## Installation

You can install the released version of PAGES from [github](https://github.io) with:

```r
# Install point from GitHub:
# install.packages("devtools")
devtools::install_github("MartinSchobben/PAGES")
```

## Usage

Load point with `library`.

```{r}
library(PAGES)
library(tidyverse)
``` 

## Data sources 

The study on the Triassic--Jurassic (~201 Ma) boundary section of Bonenburg (Germany) by @Schobben2019 is used as the example dataset in this course.


## Tidy format

A tidy format was created from the source files (look-up directory `data-raw` for details.).

```{r tidy}
head(bonenburg)
```

```{r strat}
ggplot(data = bonenburg_long, aes(x = value, y = Height)) +
  geom_line(orientation = "y") +
  facet_grid(cols = vars(measurement), scales = "free_x") +
  theme_classic()
```






# References
