---
title: "3. Patterns and models"
output: rmarkdown::html_vignette
pkgdown:
  as_is: true
vignette: >
  %\VignetteIndexEntry{model}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
bibliography: ["packages.bib", "PAGES.bib"]  
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
  )
```

```{r setup}
library(PAGES)
```


# The datasauRus and tidyverse packages

This exercise is largely constructed around the `datasauRus` [@datasauRus] package. In addition, I will use again the **tidyverse** collection packages `ggplot2` [@ggplot2; @ggplot22016] for plotting and `dplyr` [@dplyr] for data manipulations. 


```{r}
library(datasauRus)
library(ggplot2)
library(dplyr, warn.conflicts = FALSE)
```


# Data

The `datasaurus_dozen` dataset of the `datasauRus` [@datasauRus] package consists of one categorical variable `dataset` representing subsets of the data, which, in turn, all contain an `x` and `y` variable.


# Model datasauRus 

First, we will model all datasets with a conventional least square linear regression with `geom_smooth()` and by setting the argument `method` to `"lm"`. We see then that all subsets can be fitted with more-or-less similar models.


```{r model, fig.width=7, fig.height=7}
ggplot(data = datasaurus_dozen) +
  geom_smooth(mapping = aes(x = x, y = y, colour = dataset), method = "lm") +
  theme_classic() +
  theme(legend.position = "none") +
  facet_wrap(facets = vars(dataset), ncol = 3)
```


The `theme()` and `theme_classic()` functions in this construction dictate certain visual aspects of the plots. They are of no further relevance. 


# Visualize datasauRus

These plots are a variant of plots known as *Anscombe plots*, after the statistician *Francis Anscombe*, demonstrating the importance of graphing data before analysing.


```{r plot, fig.width=7, fig.height=7}
ggplot(data = datasaurus_dozen) +
  geom_point(mapping = aes(x = x, y = y, colour = dataset)) +
  theme_void() +
  theme(legend.position = "none") +
  facet_wrap(facets = vars(dataset), ncol = 3)
```


# Reference
